Reporte de inventario de eviencias

### 2022-01-04 Latex/journal_v2/HPC/main.tex
add hpc
add python

One of the goals of the next generation of mobile systems is to strictly meet the stringent QoS demands of the different services introduced in 5G , i.e., eMBB, URLLC, and mMTC. Network slicing is a promising solution to obtain the QoS for each type of service. Network slicing contains RAN slicing, core slicing, and both of them together. Efficient slicing of RAN is still challenging due to time-varying network circumstances.

In addition, according to the high complexity of RAN slicing and incapability of the traditional model-based methods, dynamic machine learning becomes the best solution for these problems.
 Generally, there are two kinds of deep reinforcement learning methods for solving dynamic problems. The first class is value-based such as Deep-Q-Network, and the second class is policy-based problems such as
deep deterministic policy gradient (DDPG). The first class can only solve the discrete action space problems, which are integer programming. The second class can solve by searching the optimal policy, which is the actor-critic method \cite{alsenwi2021intelligent,yan2019intelligent,mei2021intelligent}.
\section{Machine Learning Methods}
In this project, we want to solve the problem of dynamic resource allocation in the O-RAN system using RAN slicing. Here, we assume that we have three service types served by three slices, namely, eMBB, URLLC, and mMTC. Each service requires its specific QoS.
Our system model has a two-time scale. In the first time scale, we want to solve the problem of obtaining the optimal number of VNFs and the assignment of PRBs for each slice. In the second time scale, we seek to solve the power allocation and PRB assignment of each UEs in each slice. We use deep reinforcement learning since we want to solve the dynamic resource allocation.

@@

In this project, we would like to allocate resources using DRL. This project has a two-time scale. The first time scale considers the optimal number of VNFs and the assignment of a PRB to each slice, which is the action of our problem.
To measure the effectiveness of each state or state action pair, DQN constructs a value function model. Through optimizing the value function model, DQN derives the appropriate control policy implicitly. Although DQN has good sample efficiency and stable performance, it has the disadvantage that its action space must be a discrete variable set.

>>>>

One of the goals of the next generation of mobile systems is to strictly meet the stringent QoS demands of the different services introduced in 5G , i.e., eMBB, URLLC, and mMTC. Network slicing is a promising solution to obtain the QoS for each type of service.

In addition, according to the high complexity of RAN slicing and incapability of the traditional model-based methods, dynamic machine learning becomes the best solution for these problems.
 Generally, there are two kinds of deep reinforcement learning methods for solving dynamic problems. The first class is value-based such as Deep-Q-Network, and the second class is policy-based problems such as
deep deterministic policy gradient (DDPG). The first class can only solve the discrete action space problems, which are integer programming. The second class can solve by searching the optimal policy, which is the actor-critic method \cite{alsenwi2021intelligent,yan2019intelligent,mei2021intelligent}.
\section{Machine Learning Methods}
In this project, we want to solve the problem of dynamic resource allocation in the O-RAN system using RAN slicing. Here, we assume that we have three service types served by three slices, namely, eMBB, URLLC, and mMTC. Each service requires its specific QoS.
Our system model has a two time-scale. In the first time-scale, we want to solve the problem of obtaining the optimal number of VNFs and the assignment of PRBs for each slice. In the second time-scale, we seek to solve the power allocation and PRB assignment of each UEs in each slice. We use deep reinforcement learning since we want to solve the dynamic resource allocation.

@@

In this project, we would like to allocate resources using DRL. This project has a two time-scale. The large time-scale considers the optimal number of VNFs and the assignment of a PRB to each slice, which is the action of our problem.

\newpage
To measure the effectiveness of each state or state action pair, DQN constructs a value function model. Through optimizing the value function model, DQN derives the appropriate control policy implicitly. Although DQN has good sample efficiency and stable performance, it has the disadvantage that its action space must be a discrete variable set.
